### 2020-01-06 Source/Paper 3 - Delphi Review/DelphiEmail.tex

Round Three: Round Two’s questions will be submitted to you again but this time you will also be able to see the average reply of the other panellists and you will then be asked if you would like to adjust your answer from the second round or not. The identity of all panellists will remain confidential at all times.

The 4 questions listed below are designed to seek your personal opinion. Please reply to each one but please do not feel limited in the length or style of your answers. A reply to these by email is fine.

@@

3) The aim of creating this mobile application is to facilitate the ease with which a large number of samples can be collected? 
\begin{enumerate}[(a)]
	\item In your opinion, what problems do you foresee happening with this collection method? 
	\item Are there any potential solutions to these problems that spring to mind?
\end{enumerate}
Thanks in advance for your time,

>>>>

Round Three: The questions from the previous round will be submitted to you again but this time you will also be able to see the average reply of the other panellists and you will then be asked if you would like to adjust your answer from the second round or not. The identity of all panellists will remain confidential at all times.

The identity of all panelists will remain confidential at all times.

The 4 questions listed below are designed to seek your personal opinion. Please reply to each one but please do not feel limited in the length or style of your answers. A reply to these by email is fine.
\par
\itshape

@@

3) The aim of creating this mobile application is to facilitate the ease with which a large number of samples can be collected? 
\begin{enumerate}[(a)]
	\item In your opinion, what problems do you foresee happening with this collection method? 
	\item Are there any potential solutions to these problems that spring to mind?
\end{enumerate}

Thanks in advance for your time,
